Collapsed Cores in Globular Clusters, \\ Gauge-Boson Couplings, and AAS\TeX\ Examples

### 2014-02-27 tex/paper1/paper1.tex
paper edits, and changes so that different image file types can be written out.  mHz now supported.

Data was obtained from SDO-AIA using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data at 12 second cadence was selected in the 171\AA,
193\AA, 211\AA\ and 131\AA\ wavebands (2012-09-22 00:00 - 06:00 UT,
1800 images per waveband).  These wavebands were selected in order to
obtain a wide range of approximate temperatures in the solar corona.

The downloaded cutout data was prepared for analysis using the
SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
move the downloaded level 1.0 FITS files to level 1.5 FITS files.  All
further processing from this point was performed in the SunPy 0.4
(http://www.sunpy.org) data analysis environment.

Datacubes were formed in each waveband.  The data were
de-rotated using fractional pixel offsets relative to the first image
in the data, with the amount of offset calculated based on solar
rotation (Howard et
al. http://adsabs.harvard.edu/abs/1990SoPh..130..295H).

\section{Analysis}

>>>>

Data was obtained from SDO-AIA using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data at 12 second cadence was selected in the 171\AA
and 193\AA\ wavebands (2012-09-23 00:00 - 06:00 UT, 1800 images per
waveband).  These wavebands were selected in order to obtain a wide
range of approximate temperatures in the solar corona.

The downloaded cutout data was prepared for analysis using the
SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
move the downloaded level 1.0 FITS files to level 1.5 FITS files.  All
further processing from this point was performed in the SunPy 0.4
(http://www.sunpy.org) data analysis environment.  Images were
de-rotated to compensate for solar rotation, based on the center of
the field of view of each image.  After de-rotation, each image layer
was co-registered with the image half way through the dataset, at
approximately 03:00 UT.

\section{Analysis}\label{sec:anal}

We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - <I(t)>)/<I(t)>$.
This normalizes the emission.  Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects.  This
results in a time-series from which its Fourier power spectrum was
analyzed.

The arithmetic and geometric mean power spectra were formed from all
the time-series in each region.  A third power spectrum was created by
first summing all the data in a region, applying the
normalization/apodization procedure described above, and then
calculating the Fourier power spectrum.  These three power spectra
then summarize the Fourier power in each region, for each wavebad studied.
